\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-03-30 ase20/intro.tex
[ASE] Fixed typos in intro

Our contribution is \( \tool \), a JavaScript IR-based Semantics Extraction
Toolchain:
\begin{itemize}[leftmargin=0.5cm]
  \item \textbf{\( \tool \) is the \textit{first tool that can automatically synthesize}
    parsers and AST-IR translators directly from a language specification,
    ECMAScript.}  For syntax, we formally introduce a variant of EBNF, \( \bnfes \),
    and propose a parser generation technique with
    lookahead parsing for \( \bnfes \), which supports automatic semicolon
    insertion. For semantics, we propose semi-automatic synthesis of AST-IR
    translators assisted by compile rules because of the
    difficulty in handling the semantics written in a natural language.  Compile rules describe how
    each step of abstract algorithms is converted into our intermediate
    representation \( \ires \) designed for ECMAScript. We evaluated \( \tool \)
    with the five most recent ECMAScript versions and the current draft of the next
    ECMAScript (ES6 to ES11).   \( \tool \) automatically generated
    parsers for all versions, and automatically compiled
    \inred{XX.X}\% of the steps in abstract algorithms on average.
  \item \textbf{ Using \( \tool \), we could define the \textit{first IR-based
    formal semantics of modern JavaScript}.}  The semantics targets the
    core of ES11, and \( \tool \) successfully synthesizes its
    parser and AST-IR translator for \inred{X,XXX} out of \inred{X,XXX}
    algorithm steps.  We manually completed the missing parts of the AST-IR
    translator (\inred{XXX} steps) in \inred{XX} days.  We evaluated the correctness
    of the formal semantics using Test262~\cite{test262}, the official
    conformance test suite, and the semantics passed all \inred{XX,XXX}
    applicable tests.  Moreover, we found \inred{X} specification errors in ES11
    thanks to the formal semantics.  They were all confirmed by TC39 and will be
    fixed in the next release.
  \item \textbf{\( \tool \) is also \textit{forward compatible} with new language features
    proposed for future ECMAScript specifications.}  TC39 manages proposals of
    new language features in an open source
    project\footnote{https://github.com/tc39/proposals}.  Out of five stages
    of proposals (from Stage 0 to Stage 4), proposals in Stage 4 (Finished)
    are ready for inclusiong in the next ECMAScript, and proposals in
    Stage 3 (Candidate) are in the last stage before finished.  We
    evaluated the forward compatibility of \( \tool \) by appling it
    to all \inred{XX} proposals in Stage 3. It successfully
    synthesized parsers for all proposals, and automatically
    compiled \inred{XX} out of \inred{XX} algorithm steps for all
    proposals.  After completion of the missing parts,
    each semantics passed all \inred{XX} tests.
\end{itemize}

>>>>

Our contribution is \( \tool \), a JavaScript IR-based Semantics Extraction
Toolchain:
\begin{itemize}[leftmargin=0.5cm]
  \item \textbf{\( \tool \) is the \textit{first tool that can automatically synthesize}
    parsers and AST-IR translators directly from a language specification,
    ECMAScript.}  For syntax, we formally introduce a variant of EBNF, \( \bnfes \),
    and propose a parser generation technique with
    lookahead parsing for \( \bnfes \), which supports automatic semicolon
    insertion. For semantics, we propose semi-automatic synthesis of AST-IR
    translators assisted by compile rules because of the
    difficulty in handling the semantics written in a natural language.  Compile rules describe how
    each step of abstract algorithms is converted into our intermediate
    representation \( \ires \) designed for ECMAScript. We evaluated \( \tool \)
    with the five most recent ECMAScript versions and the current draft of the next
    ECMAScript (ES6 to ES11).   \( \tool \) automatically generated
    parsers for all versions, and automatically compiled
    \inred{XX.X}\% of the steps in abstract algorithms on average.
  \item \textbf{ Using \( \tool \), we could define the \textit{first IR-based
    formal semantics of modern JavaScript}.}  The semantics targets the
    core of ES11, and \( \tool \) successfully synthesizes its
    parser and AST-IR translator for \inred{X,XXX} out of \inred{X,XXX}
    algorithm steps.  We manually completed the missing parts of the AST-IR
    translator (\inred{XXX} steps) in \inred{XX} days.  We evaluated the correctness
    of the formal semantics using Test262~\cite{test262}, the official
    conformance test suite, and the semantics passed all \inred{XX,XXX}
    applicable tests.  Moreover, we found \inred{X} specification errors in ES11
    thanks to the formal semantics.  They were all confirmed by TC39 and will be
    fixed in the next release.
  \item \textbf{\( \tool \) is also \textit{forward compatible} with new language features
    proposed for future ECMAScript specifications.}  TC39 manages proposals of
    new language features in an open source
    project\footnote{https://github.com/tc39/proposals}.  Out of five stages
    of proposals (from Stage 0 to Stage 4), proposals in Stage 4 (Finished)
    are ready for inclusion in the next ECMAScript, and proposals in
    Stage 3 (Candidate) are in the last stage before finished.  We
    evaluated the forward compatibility of \( \tool \) by applying it
    to all \inred{XX} proposals in Stage 3. It successfully
    synthesized parsers for all proposals, and automatically
    compiled \inred{XX} out of \inred{XX} algorithm steps for all
    proposals.  After completion of the missing parts,
    each semantics passed all \inred{XX} tests.
\end{itemize}
